Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-09-10 analysis/paper/sim_survey_paper.Rmd
Add an option to plot_error_surface function for viewing results against sample size and revise presentation accordingly

$$RMSE = \sqrt{\frac{ \sum_{a = 1}^{N_a} \sum_{y = 1}^{N_y} \sum_{k = 1}^{N_k} (\hat{I}_{a,y,k} - I_{a,y})}{N_a N_y N_k}}$$
Where $N_a$, $N_y$, and $N_k$ are the number of years, ages and simulations, respectively, and $I_{a,y}$ is the true abundance available to the survey (i.e. catchability corrected abundance; $I_{a,y} = q_a N_{a,y}$). All simulations and analyses were conducted using `r substr(version$version.string, 1, 15)` [@R2017] and the code has been developed into a package called `SimSurvey` to facilitate future work and collaboration (https://github.com/PaulRegular/SimSurvey).

>>>>

$$RMSE = \sqrt{\frac{ \sum_{a = 1}^{N_a} \sum_{y = 1}^{N_y} \sum_{k = 1}^{N_k} (\hat{I}_{a,y,k} - I_{a,y})^2}{N_a N_y N_k}}$$
Where $N_a$, $N_y$, and $N_k$ are the number of years, ages and simulations, respectively, and $I_{a,y}$ is the true abundance available to the survey (i.e. catchability corrected abundance; $I_{a,y} = q_a N_{a,y}$). All simulations and analyses were conducted using `r substr(version$version.string, 1, 15)` [@R2017] and the code has been developed into a package called `SimSurvey` to facilitate future work and collaboration (https://github.com/PaulRegular/SimSurvey).

### 2018-09-10 analysis/presentation/sim_survey_presentation.Rmd
Draft a plot for visualizing relationship between sample size and error
Add an option to plot_error_surface function for viewing results against sample size and revise presentation accordingly

---
title: "Using simulation to optimize the sampling design of fisheries-independent trawl surveys"
author: "Paul M. Regular & Fran Mowbray"
date: "September 6^th^, 2018"
output:
  ioslides_presentation:
    mathjax: local
    self_contained: false
    widescreen: true
    incremental: true
    logo: dfo_logo.png
    css: dfo_style.css
bibliography: references.bib
---

@@

- Each survey was run 1000 times over the same population
- Abundance estimates, $\hat{I}_{a,y,k}$, were obtained using a stratified analysis [@Smith1981]
- Used root-mean-squared error (RMSE) as a measure of the precision and bias of the abundance estimates from each survey:
    - $RMSE = \sqrt{\frac{ \sum_{a = 1}^{N_a} \sum_{y = 1}^{N_y} \sum_{k = 1}^{N_k} (\hat{I}_{a,y,k} - I_{a,y})}{N_a N_y N_k}}$
    - Where $I_{a,y}$ is the true abundance available to the survey
- Powered by R and worked into a package (https://github.com/PaulRegular/SimSurvey)

@@

### RMSE

<dev class = "left">
```{r}
slide_font <- list(size = 14, color = rgb(121, 121, 121, maxColorValue = 255))
surface_font <- list(titlefont = slide_font, 
                     tickfont = slide_font)
surface_scene <- list(
  xaxis = surface_font,
  yaxis = surface_font,
  zaxis = surface_font
)
plot_error_surface(sim) %>% 
  tight_layout(scene = surface_scene,
               margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```
</dev>

@@

<dev class = "left">
```{r}
main_sim <- sim
load("analysis/cod_sim_exports/2018-07-16_test/test_output.RData")
plot_age_strat_fan(sim, surveys = surveys$survey,
                   ages = 2:6, years = sim$years, select_by = "age",
                   plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```
</dev>

@@

<dev class = "left">
```{r}
plot_error_surface(sim) %>% 
  tight_layout(scene = surface_scene,
               margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```
</dev>

@@

>- Bias is negligible in this scenario
>- Increases in secondary sampling does little to improve estimates

>>>>

---
title: "Using simulation to optimize the sampling design of fisheries-independent trawl surveys"
author: "Paul M. Regular & Fran Mowbray"
date: "September 12^th^, 2018"
output:
  ioslides_presentation:
    mathjax: local
    self_contained: false
    widescreen: true
    incremental: true
    logo: dfo_logo.png
    css: dfo_style.css
bibliography: references.bib
---

@@

- Each survey was run 1000 times over the same population
- Abundance estimates, $\hat{I}_{a,y,k}$, were obtained using a stratified analysis [@Smith1981]
- Used root-mean-squared error (RMSE) as a measure of the precision and bias of the abundance estimates from each survey:
    - $RMSE = \sqrt{\frac{ \sum_{a = 1}^{N_a} \sum_{y = 1}^{N_y} \sum_{k = 1}^{N_k} (\hat{I}_{a,y,k} - I_{a,y})^2}{N_a N_y N_k}}$
    - Where $I_{a,y}$ is the true abundance available to the survey
- Powered by R and worked into a package (https://github.com/PaulRegular/SimSurvey)

@@

### RMSE ~ sampling protocol

<dev class = "left">
```{r}
slide_font <- list(size = 14, color = rgb(121, 121, 121, maxColorValue = 255))
surface_font <- list(titlefont = slide_font, 
                     tickfont = slide_font)
surface_scene <- list(
  xaxis = surface_font,
  yaxis = surface_font,
  zaxis = surface_font
)
plot_error_surface(sim, plot_by = "rule") %>% 
  tight_layout(scene = surface_scene,
               margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```
</dev>

### RMSE ~ sample size

<dev class = "left">
```{r}
plot_error_surface(sim, plot_by = "samples") %>% 
  tight_layout(scene = surface_scene,
               margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```
</dev>

@@

<dev class = "left">
```{r}
main_sim <- sim
load("analysis/cod_sim_exports/2018-09-07_test/test_output.RData")
plot_age_strat_fan(sim, surveys = surveys$survey,
                   ages = 2:6, years = sim$years, select_by = "age",
                   plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```
</dev>

@@

<dev class = "left">
```{r}
plot_error_surface(sim, plot_by = "samples") %>% 
  tight_layout(scene = surface_scene,
               margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```
</dev>

@@

In this scenario,

- Bias is negligible
- Increasing sub-sampling is always benifical
- Sampling fewer fish at more locations appears better than many fish at fewer locations
